Radio Emission from Red-Giant Hot Jupiters

### 2015-09-26 ms.tex
Fixed units of sigma-rms in sensitivity table.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{deluxetable*}{cccccc}
\tabletypesize{\footnotesize}
\tablecolumns{6}
\tablecaption{Detectability of Hot Jupiters with Current 
and Future Radio Telescopes.\label{tab:sens}}
\tablehead{
Instrument & Band  & \sigRMS\tablenotemark{a} & $\tau$\tablenotemark{b}  & Resolution & $\sigma_c$\tablenotemark{c}\\
           & (MHz) & ($\mu$Jy~hr$^{1/2}$)         &  (hr)                    & (\arcsec)  & ($\mu$Jy bm$^{-1}$)} 
\startdata
LOFAR-LBA  &  30-80  & 1100  & 230000             & 10   & 57 \\ 
LOFAR-HBA  & 110-200 & 180   &   6500             & 4.1  & 1.1 \\  
HERA       & 50-250  &  76   & 1200               & 410  & 36000\\ 
GMRT       & 130-190 & 162   &   5400             & 16.5 & 57 \\ 
%LWA       &  30-80  & 50000 &  702127141         & 10.3 & 42.2 \\
%MWA       &  30-80  & 24000 &  176223211         & 1030 & 4.2$\times10^5$ \\
SKA-Low (part) & 50-200 & 5.9 &   7.2             & 7.6  & 9.7 \\
SKA-Low (full) & 50-350 & 1.8 &  0.7              & 4.8  & 1.5 \\
%VLA 4-Band& 30-80   & 3300  & 2312058            & 28.6 & 330 \\
VLA-LOBO   &  50-350 &  77   &  1200              & 8.6  & 10.4
\enddata
%\tablecomments{Time estimates to reach 2~$\mu$Jy RMS.}
\tablenotetext{a}{RMS noise in a 1-hour observation, computed for imaging of the full band reported 
in this table (Equation~\ref{eq:rms_sens}).}
\tablenotetext{b}{The integration time in hours required to reach an RMS of 2~$\mu$Jy (i.e.\ 5-$\sigma$ detection
of a typical source at 100~pc with 10~$\mu$Jy bm$^{-1}$ average flux).}
\tablenotetext{c}{Source confusion RMS contribution.}
\end{deluxetable*}
%
% HERA
% http://reionization.org/wp-content/uploads/2015/05/HERA0_imaging.pdf
%
% LOFAR
% https://www.astron.nl/~heald/test/sens.php; 
% 24 core stations, 16 remote, 8 international, 488 subbands
%
% GMRT
% http://gmrt.ncra.tifr.res.in/~astrosupp/obs_setup/sensitivity.html
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{deluxetable*}{cccccc}
\tabletypesize{\footnotesize}
\tablecolumns{6}
\tablecaption{Detectability of Hot Jupiters with Current 
and Future Radio Telescopes.\label{tab:sens}}
\tablehead{
Instrument & Band  & \sigRMS\tablenotemark{a} & $\tau$\tablenotemark{b}  & Resolution & $\sigma_c$\tablenotemark{c}\\
           & (MHz) & ($\mu$Jy bm$^{-1}$)         &  (hr)                    & (\arcsec)  & ($\mu$Jy bm$^{-1}$)} 
\startdata
LOFAR-LBA  &  30-80  & 1100  & 230000             & 10   & 57 \\ 
LOFAR-HBA  & 110-200 & 180   &   6500             & 4.1  & 1.1 \\  
HERA       & 50-250  &  76   & 1200               & 410  & 36000\\ 
GMRT       & 130-190 & 162   &   5400             & 16.5 & 57 \\ 
%LWA       &  30-80  & 50000 &  702127141         & 10.3 & 42.2 \\
%MWA       &  30-80  & 24000 &  176223211         & 1030 & 4.2$\times10^5$ \\
SKA-Low (part) & 50-200 & 5.9 &   7.2             & 7.6  & 9.7 \\
SKA-Low (full) & 50-350 & 1.8 &  0.7              & 4.8  & 1.5 \\
%VLA 4-Band& 30-80   & 3300  & 2312058            & 28.6 & 330 \\
VLA-LOBO   &  50-350 &  77   &  1200              & 8.6  & 10.4
\enddata
%\tablecomments{Time estimates to reach 2~$\mu$Jy RMS.}
\tablenotetext{a}{RMS noise in a 1-hour observation, computed for imaging of the full band reported 
in this table (Equation~\ref{eq:rms_sens}).}
\tablenotetext{b}{The integration time in hours required to reach an RMS of 2~$\mu$Jy (i.e.\ 5-$\sigma$ detection
of a typical source at 100~pc with 10~$\mu$Jy bm$^{-1}$ average flux).}
\tablenotetext{c}{Source confusion RMS contribution.}
\end{deluxetable*}
%
% HERA
% http://reionization.org/wp-content/uploads/2015/05/HERA0_imaging.pdf
%
% LOFAR
% https://www.astron.nl/~heald/test/sens.php; 
% 24 core stations, 16 remote, 8 international, 488 subbands
%
% GMRT
% http://gmrt.ncra.tifr.res.in/~astrosupp/obs_setup/sensitivity.html
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
